% This file was converted to LaTeX by Writer2LaTeX ver. 0.5.0.2
% see http://www.hj-gym.dk/~hj/writer2latex for more info
\documentclass{article}
\usepackage[ascii]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{amsmath,amssymb,amsfonts,textcomp}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{pdftex, colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, pagecolor=blue, urlcolor=blue, pdftitle=William G Keys, pdfauthor=Office 2004 Test Drive User, pdfsubject=, pdfkeywords=}
% Text styles
\newcommand\textstyleInternetlink[1]{\textcolor{blue}{#1}}
% Outline numbering
\setcounter{secnumdepth}{0}
% List styles
\newcommand\liststyleWWviiiNumvi{%
\renewcommand\labelitemi{[F0B7?]}
\renewcommand\labelitemii{${\circ}$}
\renewcommand\labelitemiii{${\blacksquare}$}
\renewcommand\labelitemiv{[F0B7?]}
}
\newcommand\liststyleWWviiiNumvii{%
\renewcommand\labelitemi{[F0B7?]}
\renewcommand\labelitemii{${\circ}$}
\renewcommand\labelitemiii{${\blacksquare}$}
\renewcommand\labelitemiv{[F0B7?]}
}
\newcommand\liststyleWWviiiNumv{%
\renewcommand\labelitemi{[F0B7?]}
\renewcommand\labelitemii{${\circ}$}
\renewcommand\labelitemiii{${\blacksquare}$}
\renewcommand\labelitemiv{[F0B7?]}
}
\newcommand\liststyleWWviiiNumii{%
\renewcommand\labelitemi{[F0B7?]}
\renewcommand\labelitemii{[F081?]}
\renewcommand\labelitemiii{${\blacksquare}$}
\renewcommand\labelitemiv{[F06C?]}
}
\newcommand\liststyleWWviiiNumiii{%
\renewcommand\labelitemi{[F0B7?]}
\renewcommand\labelitemii{[F081?]}
\renewcommand\labelitemiii{${\blacksquare}$}
\renewcommand\labelitemiv{[F06C?]}
}
% Page layout (geometry)
\setlength\paperwidth{8.5in}
\setlength\paperheight{11in}
\setlength\voffset{-1in}
\setlength\hoffset{-1in}
\setlength\topmargin{0.7in}
\setlength\oddsidemargin{0.7in}
\setlength\textheight{9.8in}
\setlength\textwidth{7.1000004in}
\setlength\footskip{0.0cm}
\setlength\headheight{0cm}
\setlength\headsep{0cm}
% Footnote rule
\setlength{\skip\footins}{0.0469in}
\renewcommand\footnoterule{\vspace*{-0.0071in}\setlength\leftskip{0pt}\setlength\rightskip{0pt plus 1fil}\noindent\textcolor{black}{\rule{0.25\columnwidth}{0.0071in}}\vspace*{0.0398in}}
% Pages styles
\makeatletter
\newcommand\ps@Standard{
  \renewcommand\@oddhead{}
  \renewcommand\@evenhead{}
  \renewcommand\@oddfoot{}
  \renewcommand\@evenfoot{}
  \renewcommand\thepage{\arabic{page}}
}
\makeatother
\pagestyle{Standard}
\title{William G Keys}
\begin{document}
\clearpage\setcounter{page}{1}\pagestyle{Standard}
\section[\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ William G.
Keys Jr.    
]{\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ William G. Keys Jr.
    }
{\selectlanguage{english}\sffamily
2 Hidden Dr.
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ Cell:
\ \ \ (845) 519-5868}

{\selectlanguage{english}\sffamily
Monroe, NY 10950
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \href{mailto:yzrider261@gmail.com}{\textstyleInternetlink{William.Keys1@marist.edu}}
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ Home: (845)
783-2689 }

\name{Christopher J. Paciorek \vspace*{.1in}}
\bigskip

[Warning: Draw object ignored]


\bigskip

{\selectlanguage{english}\sffamily\bfseries
EDUCATION}


\bigskip

{\selectlanguage{english}\sffamily
\textbf{\ \ \ \ \ \ Master of Science, Computer Science,} (Graduation
Expected, December 2010)}

{\selectlanguage{english}\sffamily
\ \ \ \ \ \ Marist College, Poughkeepsie, NY}

{\selectlanguage{english}\sffamily
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ Overall GPA: 3.45}


\bigskip

{\selectlanguage{english}\sffamily
\textbf{\ \ \ \ \ \ Bachelor of Science, Computer Science, }(December
2006) }

{\selectlanguage{english}\sffamily
\textbf{\ \ \ \ \ \ }Plattsburgh State University, Plattsburgh, NY}

{\selectlanguage{english}\sffamily
\ \ \ \ \ \ Major: Computer Science, Minor: Math \ \ \ \ \ \ }

{\selectlanguage{english}\sffamily
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ Major GPA: 3.15 Overall GPA: 3.05
\ \ \ \ \ \ \ \ \ \ \ \ \ \ }


\bigskip

{\selectlanguage{english}\sffamily\bfseries
PRESENTATIONS}


\bigskip

{\selectlanguage{english}\sffamily
\textbf{\ \ \ \ \ \ Computer Science and Math Seminar, }SUNY
Plattsburgh}

{\selectlanguage{english}\sffamily
\ \ \ \ \ \ {\textquotedblleft}Implementing Minimal Spanning Trees
Efficiently{\textquotedblright} April 2006 \ \ }


\bigskip

{\selectlanguage{english}\sffamily\bfseries
TECHNICAL SKILLS}


\bigskip

\liststyleWWviiiNumvi
\begin{itemize}
\item {\selectlanguage{english}\sffamily
C/C++, Perl, Java, Python, PHP, SQL, HTML, CSS, XML, BASH}
\end{itemize}
\liststyleWWviiiNumvii
\begin{itemize}
\item {\selectlanguage{english}\sffamily
Linux, Windows XP/Vista, Mac OS X}
\item {\selectlanguage{english}\sffamily
Apache, MySQL, Bind, Joomla, Wordpress, Nagios, Amavis, ClamAV and
Sophos, Vmware,KVM, SELinux, Iptables, RPM, SSH, CVS, Git, Samba,
Eclipse, UNIX utilities, Microsoft Office}
\end{itemize}
\liststyleWWviiiNumv
\begin{itemize}
\item {\selectlanguage{english}\sffamily
RAID Disk Arrays, PC{\textquotesingle}s, Networking (HTTP, DNS, FTP)}
\end{itemize}

\bigskip

{\selectlanguage{english}\sffamily\bfseries
PROFESSIONAL EXPERIENCE}


\bigskip

{\selectlanguage{english}\sffamily
\textbf{\ \ \ \ \ \ Developer / Network Administrator, }Guardian
Digital, Allendale NJ, 2007-2009  }

\liststyleWWviiiNumii
\begin{itemize}
\item {\selectlanguage{english}\sffamily
Managed development, implemented, updated, maintained three corporate
websites.}
\end{itemize}
{\selectlanguage{english}\sffamily
\href{http://www.linuxsecurity.com/}{\textstyleInternetlink{www.linuxsecurity.com}},
www.guardiandigital.com and www.engardelinux.org}

\liststyleWWviiiNumii
\begin{itemize}
\item {\selectlanguage{english}\sffamily
Redesigned company{\textquotesingle}s Web site to make it more visually
appealing to users. Increased Ad revenue by 112\%. Utilized SEO
techniques.}
\item {\selectlanguage{english}\sffamily
Created and deployed scripts for being more proactive in maintaining an
email server.}
\item {\selectlanguage{english}\sffamily
Developed a Perl script to automate the process of archiving various
server backups. \ \ \ \   \ \ \ \ \ \ \ \ \ \ }
\item {\selectlanguage{english}\sffamily
Member of a team of developers implementing a e-commerce Secure Linux
Server Operating System. Improved quality and assurance phase of
development by automating many of the testing cases. \ Added new user
interface to increase user-ability and functionality.}
\item {\selectlanguage{english}\sffamily
Built several test networks with VMware to simulate live environments
for testing.}
\item {\selectlanguage{english}\sffamily
Took the role of training new employees.}
\end{itemize}

\bigskip

{\selectlanguage{english}\sffamily\bfseries
PUBLICATIONS}


\bigskip

\liststyleWWviiiNumiii
\begin{itemize}
\item {\selectlanguage{english}\sffamily
Co-Author, {\textquotedblleft}Recipe for a Secure
Server,{\textquotedblright} \textit{Linux + DVD Magazine}, March 2007}
\item {\selectlanguage{english}\sffamily
Co-Author, {\textquotedblleft}Demystifying the Power of
SELinux,{\textquotedblright} \textit{Haking Magazine,} May 2007}
\end{itemize}

\bigskip

{\selectlanguage{english}\sffamily\bfseries
RELATED EXPERIENCE}


\bigskip

{\selectlanguage{english}\sffamily
\textbf{\ \ \ \ \ \ Network Administrator Internship,} Plattsburgh State
University\textbf{, }Fall 2006}

{\selectlanguage{english}\sffamily
Implemented Perl scripts to automate task for maintaining the
lab{\textquotesingle}s Linux machines.
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ }
{\selectlanguage{english}\sffamily
Developed a Perl web application to make managing campus firewalls
easier. \ }
\section[Provided troubleshooting for PostgreSQL database running on
Linux.
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ ]{\textmd{Provided
troubleshooting for PostgreSQL database running on Linux.}
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ }

\bigskip
\end{document}
